CommonMind Consortium: DLPFC

### 2020-09-16 combined_analysis/combine_all_DLPFC.Rmd
bug fixes

### Only autosomes
```{r show.gene_set_test.marginal.Sex.autosome, eval=TRUE}
show_zenith_results( res_meta_zenith.sex_autosome, "Reported_GenderMale", "GO", FDR=0.05) 
show_zenith_results( res_meta_zenith.sex_autosome, "Reported_GenderMale", "MSigDB", FDR=0.05)   
```

>>>>

### Only autosomes
```{r show.gene_set_test.marginal.Sex.autosome, eval=TRUE}
show_zenith_results( res_meta_zenith.sex_autosome, "Reported_GenderMale", "GO", FDR=0.1) 
show_zenith_results( res_meta_zenith.sex_autosome, "Reported_GenderMale", "MSigDB", FDR=0.1)   
```
